\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{lstlisting}{0}

\chapter{Data Log Format}
\label{log}
\minitoc

A basic exocentric vision system for \morduc{} would need, 
at least, some images captured from the camera mounted 
on top of it and, for each image, the actual position of 
the robot at the time it was captured.
\\
While images could be used as a texture on which draw 
a 3d representation of the robot, information about 
position are essential in order to draw the robot 
consistently, i.e. in the position the observer would 
see it if he was seeing the robot by means of an actual 
external camera.
\\
Images and data can be read from different kind of source 
information. If we want to interact in `on-line' mode with
the robot, they are sent through the Internet network;
otherwise, images and robot's odometric data can be
obtained by previous log session stored into a predefined
path in our disk.
\\
It is now only briefly reported that
\framework{} can interact with different type of source
information, by means of the \textit{IDataLogic} interface.
Further explanations will be supplied later on this in this
document (chapter \ref{rear}).
\\
In this section two different kind of log information are
exposed. The first is obtained by guiding the robot through
a simulator program, able to recreate the demanded environment
where a \morduc{} replica can move in. All images (as seen by
the robot virtual camera) and data are collected and stored
during the simulation running, so \framework{} can retrieve
its information from static files.
\\
The second category of log information \framework{} can base
its computation on are derived from real \morduc{} teleguiding
session. When controlled by any remote client (\framework{}
itself or a completely different one, even a web browser),
\morduc{} can save image and odometric data captured after changing
its status (i.e. moving or turning).
\\
Making \framework{} able to work with information contained in
static file has proved to be highly important in development.
We can not have \morduc{} always powered on, connected to the
network and free to move in any direction, simply because
we want to test a specific feature of our client program. Moreover,
the condition we want to test our feature with could be not easy
or immediate to recreate in real word, for whatever physical
impediment or constriction. It could happen that a specific robot
path must be repeated more times, always the same, to verify
different proposed solutions.
\\
The core algorithm encapsulated in \framework{} can be test
on real online session as well as with offline data, that 
makes all the development phase easer.


\clearpage
\input{log_format/morduc_simulator_log}

\clearpage
\input{log_format/morduc_log}
