\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{lstlisting}{0}

\section{Introducing OpenGL}
\label{sec:opengl}
\lstset{language=C++}

OpenGL is designed as a software interface to the graphics 
hardware on your computer. It defines a platform-independent API;
the API is then implemented in software and/or hardware for 
various machine architectures. The advantage is that OpenGL 
programs are easily portable to a variety of computers. 
OpenGL provides basic commands to support rendering. 
In particular, OpenGL doesn't provide functionality to support
windows or user interaction (like keyboard presses or mouse 
actions); these features are provided by a separate library called
GLUT (the OpenGL Utility Toolkit). GLUT also provides some 
higher-level features, such as more complex geometrical objects.
\\
OpenGL is a state machine, which means that you specify various 
states or modes which remain in effect until changed.
Each command that is executed is carried out within the current 
state. States include things like the current window (where
drawing will appear), colour, viewing and projection matrices, 
drawing modes, positions and characteristics of lights,
materials, and features. These elements will not be introduced 
throughout this document, as they are already explained in
various tutorials \cite{opengl:brieftutorial} o manual books 
\cite{opengl:redbook}.
\\
Nevertheless, it is important to keep the idea of a 
"state machine" in mind as you work with OpenGL in order to 
understand the effects of a given command. The current state 
is not reset when a function starts or ends - the current state
is in effect until something changes it, regardless of where 
in the program the next thing is. 
\\
In the following, we are going to analyse some peculiar 
aspects of OpenGL. Anyway, this chapter is not intended 
to be an exhaustive guide to OpenGL programming 
- like \cite{opengl:distilled}, \cite{opengl:redbook}, but,
instead, as a collection of short how-to regarding the 
aspects of OpenGL which we have dealt with the most 
during our work. 

\newpage
\input{opengl/opengl_note}
\newpage
\input{opengl/setting_texture}
\newpage
\input{opengl/light_opengl}
\newpage
\input{opengl/perspective_opengl}
